\section*{\Huge Abstract}

\vspace{0.7cm}

\begin{spacing}{1.25}
This report presents the work carried out as part of my Final Year Project, focusing on the design, development, and deployment of FinderrLink, a web platform dedicated to connecting freelancers, companies, and agencies. The project aims to facilitate mission search, professional profile management, application tracking, and communication between the different users of the platform.

FinderrLink is based on a modern full-stack architecture composed of a dynamic frontend, a structured backend, and a relational database. The platform includes several functional modules such as user management, freelancer profiles, mission management, applications, messaging, notifications, dashboards, and an intelligent assistant designed to improve the user experience.

An important aspect of the project is the implementation of an RBAC system, or Role-Based Access Control, which manages access rights according to each user’s role. Freelancers, companies, agencies, and administrators each have specific interfaces, permissions, and features adapted to their needs. This system improves security, ensures a clear separation of responsibilities, and provides consistent access management across the application.

The project also covers the deployment phase in a server environment, including application service configuration, database management, reverse proxy setup, access security, and preparation of the platform for production use.
\end{spacing}

\vspace{0.4cm}
\noindent \textbf{Keywords:} FinderrLink, Full-stack development, Web deployment, Web platform, Freelancer, Company, Agency, RBAC, Missions, Applications, Messaging, Notifications, Artificial intelligence, API, Database.
